Automated topic naming to support analysis of software maintenance activities

### 2010-08-19 icse/icse2011.tex
version for Jorge

\documentclass[]{sig-alternate}
 \usepackage{booktabs}
\usepackage[caption=false]{subfig}
 \usepackage[colorinlistoftodos,backgroundcolor=yellow]{todonotes} %disable
 \usepackage{color}

@@

For example, in Fig. \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have more intense shaded boxes.

@@

\section{Conclusions and future work}
%\todo[inline]{Need to juxtapose our work against previous work -- contribution}

>>>>

\documentclass[]{sig-alternate}
 \usepackage{booktabs}
\usepackage[caption=false]{subfig}
 \usepackage[colorinlistoftodos,backgroundcolor=yellow,disable]{todonotes} %disable
 \usepackage{color}

@@

For example, in Fig. \ref{fig:mysql-timeline}, we see that the NFRs \emph{functionality}, \emph{portability} and \emph{maintainability} contain more labeled topics, since these NFRs have more intensely shaded boxes. We note that the gap in the MaxDB data is due to an interruption in the source data, having to do with the infrastructure for releasing data, rather than specific occurrences in the project.
\todo[inline]{can I pin this down more ?}

\todo[inline]{try to pin down these reasons below}%  MySQL 3.23 was put on maintenance.
% 
% MySQL forks repositories per every version and 3.23 was supported for a
% long time. there was 4.0 4.1 5.0 5.1
% 
% This is the MySQL 3.23 branch
% 
% Same thing with MaxDB 7.5
% 7.6 is in a different repository

@@

\section{Conclusions and future work}
%\todo[inline]{Need to juxtapose our work against previous work -- contribution}
\todo[inline]{tighten... typically conclusions are much shorter.}
